My title

### 2023-10-23 outputs/paper/paper.qmd
Update the introduction and data part

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  
\[
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
\]
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

# References
https://news.un.org/en/story/2023/05/1136367
https://www.aljazeera.com/news/2023/5/11/three-years-1-1-million-deaths-covid-emergency-ending-in-us

>>>>

In this paper, there are three main sources of data, which are American Community Survey (ACS), The Center for Systems Science and Engineering (CSSE) at John-Hopkins University, Fox News. These three sources contains different dimensional data in predicting the death rate of COVID in each county.

## American Community Survey (ACS)

The data from ACS contains the socio-economic information for each county. While there are many tables from ACS, I will only take three of them which are DP02, DP03 and DP05. All the tables are the 2021 five-year ACS estimates

For DP02, it contains the data regarding the social characteristics. In this paper, I will only take the information regarding the educational attainment such as the percentage of residents in each county that have at a least bachelor degree. Compared to DP02, DP03 contains the information about the economic characteristics. To understand the deaths rate in terms of economy, I will grab the information about the proportion of residents with a private insurance, the mean household income and unemployment rate at each county. Finally, DP05 contains the demographic data and housing estimates. In this paper, I will take the total population, proportions of children and people above 85 and percentage of white and black residents.

## CSSE at JHU
The CSSE at JHU collects the worldwide COVID data since 2020 to 2023. All the raw data are available on their CSSE GitHub which can easily access. In particular, the COVID daily report since 2020 for each county on US are listed. However, they stop to update the data after March 9th, 2023 as no significant changes. The COVID data for US used in the paper is data collected on March 9th.

In the data on March 9th, it contains the number of confirmed cases and deaths for each county in US, as well as the incident rate. To perform the data analysis later in this paper, I will only use the COVID cases and deaths in each county.

## Fox News
It contains the county-level election results during the 2020 Federal Election. For each county, it contains the number of votes for the demographic and republican party

@@

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.\
\[ \begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align} \] We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

# References

https://news.un.org/en/story/2023/05/1136367 https://www.aljazeera.com/news/2023/5/11/three-years-1-1-million-deaths-covid-emergency-ending-in-us
